\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-23 metatheory.tex
Reply all the comments. Please check.
FIx language: distinguish judgement and the derivation of the judgement.

The reason we choose this version of predicative MLTT is mainly because it is simpler on the formulation and metatheoretical reasoning, easy to extend and is enough as a background for setting up the formalization of the key feature for our language, like overriding and inheritance about the families. Compared to a more complete Coq's formal foundation like \textit{Predicative Calculus of Cumulative Inductive Constructions}~\cite{timany2018cumulative}, our formulation lacks cumulativity (though our formulation still has multi-level universe) and impredicative universe (the \mintinline{Coq}{Prop : Type}). \YZ{
    What's the relation to the CIC underlying Coq, given that the implementation is a Coq plugin?
}\EDJreply{Add the comparison between this version of predicative MLTT and PCUIC. Please Check.}
% Thus we will omit a great deal of details about MLTT here

@@

Our formulation can be seen as following the practice ``type theory should eat itself''\cite{dybjer1995internal, chapman2009type}. We use as the formulation the intrinsically-typed debruijn syntax in this type-theoretical QIIT instead of a more conventional and untyped representation, because (1) we hope our formulation can be precise on the mathematical object we are using (2) it is easier to validate a pen-and-paper proof now because proof checking then is simply type checking in type theory (3) when using QIIT to formulate syntax, the induction principle used in reasoning about syntax is itself justified (4) we hope our formulation can be closer to a real mechanized one so that the reader can have an idea about how mechanization can be carried out (5) We can still use named-variables for intuition and example illustration (6) using QIIT as syntax encoding can avoid the reader from the concept of \textit{presupposition}~\cite{gratzer-sterling-birkedal-2019}---these \textit{presupposition} can be understood as \textit{implicit parameters} of the declaration of the judgemental rules in QIIT.

>>>>

The reason we choose this version of predicative MLTT is mainly because it is simpler on the formulation and metatheoretical reasoning, easy to extend and is enough as a background for setting up the formalization of the key feature for our language, like overriding and inheritance about the families. Compared to a more complete Coq's formal foundation like \textit{Predicative Calculus of Cumulative Inductive Constructions}~\cite{timany2018cumulative}, our formulation lacks cumulativity (though our formulation still has multi-level universe) and impredicative universe (the \mintinline{Coq}{Prop : Type}). \YZ{
    What's the relation to the CIC underlying Coq, given that the implementation is a Coq plugin?
}\EDJreply{Add the comparison between this version of predicative MLTT and PCUIC. Please Check. }
% Thus we will omit a great deal of details about MLTT here

@@

Our formulation can be seen as following the practice ``type theory should eat itself''\cite{dybjer1995internal, chapman2009type}. We use as the formulation the intrinsically-typed debruijn syntax in this type-theoretical QIIT instead of a more conventional and untyped representation, because (1) we hope our formulation can be precise on the mathematical object we are using (2) it is easier to validate a pen-and-paper proof now because proof checking then is simply type checking in type theory (3) when using QIIT to formulate syntax, the induction principle used in reasoning about syntax is itself justified (4) we hope our formulation can be closer to a real mechanized one so that the reader can have an idea about how mechanization can be carried out (5) We can still use named-variables for intuition and example illustration (6) using QIIT as syntax encoding can avoid the reader from the concept of \textit{presupposition}~\cite{gratzer-sterling-birkedal-2019}---these \textit{presupposition} can be understood as \textit{implicit parameters} of the declaration of the typing rules in QIIT.

### 2022-10-23 standardmodel.tex
FIx language: distinguish judgement and the derivation of the judgement.

We again encourage the reader to read the (pseudo-)Agda-style proof mentioned in our appendix because most of the parts are similar but with more type annotation so it is clearer about the mathematical object doing the interpretation. Here, we need to clarify some ambiguity in our conventional formulation. For example, when we wrote ``$\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ defined inductively on $\denotesS{\Sigma}$'', the best way to understand is to consider we are defining a function $\denotesS{\goodType{\Gamma}{\cC \_}{}}$ as the interpretation for $\goodType{\Gamma}{\cC \_}{}$ that mapping $\denotesS{\sigma}$ to $\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ also defined inductively on the length of the signature. The case is similar for $\denotesS{\cL \_}$, $\denotesS{\cCt \_}$ and  $\denotesS{\Sigma \ \_ \ \_}$. \textbf{This is actually the formulation in Agda}---QIIT syntax consider $\cC : "Sig"~\Gamma~n \to "Ty"~\Gamma$ as a constructor and our model needs to interpret this constructor to a function $\cC^S : "Sig"^S \Gamma^S~n \to "Ty"^S~\Gamma^S$ with each judgement type also interpreted.

>>>>

We again encourage the reader to read the (pseudo-)Agda-style proof mentioned in our appendix because most of the parts are similar but with more type annotation so it is clearer about the mathematical object doing the interpretation. Here, we need to clarify some ambiguity in our conventional formulation. For example, when we wrote ``$\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ defined inductively on $\denotesS{\Sigma}$'', the best way to understand is to consider we are defining a function $\denotesS{\goodType{\Gamma}{\cC \_}{}}$ as the interpretation for $\goodType{\Gamma}{\cC \_}{}$ that mapping $\denotesS{\sigma}$ to $\denotesS{\goodType{\Gamma}{\cC \sigma}{}}$ also defined inductively on the length of the signature. The case is similar for $\denotesS{\cL \_}$, $\denotesS{\cCt \_}$ and  $\denotesS{\Sigma \ \_ \ \_}$. \textbf{This is actually the formulation in Agda}---QIIT syntax consider $\cC : "Sig"~\Gamma~n \to "Ty"~\Gamma$ as a constructor and our model needs to interpret this constructor to a function $\cC^S : "Sig"^S \Gamma^S~n \to "Ty"^S~\Gamma^S$ with each judgement also interpreted.

### 2022-10-23 syn-translate.tex
Fix notation.
Reply some comments.
Adding Syn Translation
FIx language: distinguish judgement and the derivation of the judgement.

Basically, we can compile away the judgement $\goodSig{\Gamma}{v}{n}$,
the type $\cL$ and $\cC$, and related terms, by transforming them into
corresponding $\Sigma$-types.

\newcommand{\denotesT}[1]{{{\llbracket {#1} \rrbracket}_T}}
\newcommand{\Sigr}[2]{{ "Sig"^r~{#1}~{#2} }}

We use $\denotesT{}$ as the translation. This translation is invariant\YZ{What does "invariant" mean?}
under the subpart. Since we are in an intrinsic setting, everything here
is well-typed (well-formed)including this translation. Thus
$\denotesT{T}$ means the same as $\denotesT{\goodType{\Gamma}{T}{}}$
(i.e. every type is tracking its context). In other words, every
derivation of any judgement will track its ``context''. This will be
clearer in the (pseudo-)Agda formalization.

>>>>

Basically, we can compile away (the derivation of) judgement $\goodSig{\Gamma}{v}{n}$,
the type $\cL$ and $\cC$, and related terms, by transforming them into
corresponding $\Sigma$-types.

% \newcommand{\denotesT}[1]{{{\llbracket {#1} \rrbracket}_T}}
% \newcommand{\Sigr}[2]{{ "Sig"^r~{#1}~{#2} }}

We use $\denotesT{}$ as the translation. This translation behaves like identity\YZ{What does "invariant" mean?}\EDJreply{behaves like identity. Sorry I should have said "subpart is invariant under this translation" instead}
under the subpart. Since we are in an intrinsic setting, everything here
is well-typed (well-formed)including this translation. Thus
$\denotesT{T}$ means the same as $\denotesT{\goodType{\Gamma}{T}{}}$
(i.e. every type is tracking its context). In other words, every
derivation of any judgement will track its ``context''. This will be
clearer in the (pseudo-)Agda formalization.

### 2022-10-23 syntax.tex
FIx language: distinguish judgement and the derivation of the judgement.

\begin{figure}[!htb]
  \begin{align*}
    &\Gamma~:~"Con"&&\mathboxtext{\goodCtx{\Gamma}{}} &&T~:~"Ty"~\Gamma&&\mathboxtext{\goodType{\Gamma}{T}{}}  &&\gamma~:~"Tms"~\Gamma~\Delta&&\mathboxtext{\goodSub{\Gamma}{\gamma}{\Delta}}  && t~:~"Tm"~\Gamma~T&&\mathboxtext{\goodTerm{\Gamma}{t}{T}} 
  \end{align*}
\caption{Judgement forms, as Agda types and as presented in this section.}\label{fig:vanillaMLTTjudgeQIIT}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Tm]
      {\goodCtx{\Gamma}{i} \quad \goodType{\Gamma}{T}{j}}
      {\goodTerm{\Gamma}{\_}{T}}
      $$
      $$
      \Rule[name=Tms]
      {\goodCtx{\Gamma}{i} \quad \goodCtx{\Delta}{i}}
      {\goodSub{\Gamma}{\_}{\Delta} \text{ is well-formed}}
      $$
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Con   : Set 
      data Ty    : Con → Set   
      data Tms   : Con → Con → Set 
      data Tm    : (Γ : Con) → Ty Γ  → Set 
    \end{minted}
  \end{minipage}

\caption{Well-formedness rules of the judgements}\label{fig:vanillaMLTTjudgewellformed}
\end{figure}
\underline{\textit{\textbf{Judgements and Universe.}}}
% Judgements in QIIT
We formalize our language as a deep embedding in a type theory using QIIT types. Every judgement is a (dependent) QIIT \textit{type} and all judgement derivations are well-typed QIIT terms. (Otherwise how can they be encoded in Agda?) There are four standard judgement forms from (vanilla) MLTT,
well-typed contexts $\goodCtx{\Gamma}{l}$, well-typed types
$\goodType{\Gamma}{T}{l}$, well-typed terms $\goodTerm{\Gamma}{t}{T}$, and
well-typed substitutions $\goodSub{\Gamma}{\gamma}{\Delta}$. The QIITs corresponding of these four judgements are
mutually recursively defined together, and declared in \cref{fig:vanillaMLTTjudgeQIIT}. Our presentation
follows the style of~\citet{kaposi2019gluing} and thus a predicative MLTT, but for readability we
omit the universe levels.
%\YZ{What's the distinction of judgments vs. sequents?}.\EDJreply{I am not sure about the correct terminology here. Here I want to say "even underivable judgement has to be well-typed". That's the main reason I spell out the (pseudo) Agda code there. I actually want the reader to have intrinsic-typed syntax in mind all the time (like read conventional math but acknowledge we are manipulating Agda)}\EDJreply{I rephrase that so there won't be confusion for the future readers. Please check}
Latex-wise, in \cref{fig:vanillaMLTTjudgewellformed}, we spell out these \textit{well-formedness rules} of type
judgements and their (pseudo-)Agda counterparts to make things more accessible. In (pseudo-)Agda, well-formedness rules are just well-typedness of (indexed) QIIT family---(the judgement)"Tm~$\Gamma$~$T$" is well-typed (well-formed) only when $\Gamma$ and $T$ are both well-typed (well-formed). We omitted a bunch for latex version. Of
course, a well-formed judgement is not necessarily derivable, just as
a well-formed QIIT type is not necessarily inhabited. 
These well-formedness rules are direct translations of the \textit{well-typedness} of QIIT.

@@

% How judgemental equality is used
Quotient is used to represent definitional equality (aka judgemental
equality) between QIIT types concisely.
This way, for all four kinds of judgements we are
using, there is always equality among these data but only those equalities between terms and types are emphasized due to their non-triviality.

@@

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma~|~"RecSig"~\tau~T \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma~|~"RecSig1"~A~B~T~|\\
    \text{Terms, including Seal}   \quad & t, t_1, t_2, f    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t~|\\ & &&"prjR"~j~o~|~"Wrec"~t_1~t_2~|~"inh"~h~t\\
    \text{Inheritance Structure} \quad & h, h' &&= "inhid"~|~"inhov"~h~t~|~"inhext"~h~t~|~"inhinh"~h~|~"inh"~h~|~"inhnest"~h~h'
  \end{alignat*}\YZ{ What is 'W T'? Do you mean 'c T'?  }\YZreply{Why is Seal not merged into Terms?}\EDJreply{You can see \ruleref{Ind-Type}. For $T : \bW\tau$, $W~T : \cU$, for $\goodType{\Gamma}{T}{}$, $c~T : \cU$ }\EDJreply{Seal can easily mergedd into terms. But seal has a new judgement. Do you want to merge them? }
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

The core language builds on MLTT and adds four new judgement forms.
% Among them, sealing judgement $\goodSeal{\Gamma}{\_}{\sigma}{A}$ is just a
% shorthand for term judgement
% $\goodTerm{\Gamma , \cC \sigma}{\_}{A[\pi_1]}$ where $A$ is a type.
% We have shown some exemplar rules for all four standard types of
% judgments. Now we focus on the newly introduced facility. 
We have two kinds of signatures, one for inductive types, the other for linkages. We start with inductive type signature.

@@

\caption{Seal Judgement, and its Agda Representation (or What do we mean when we say one judgement is a shorthand for the other)}

@@

Next we talk about inheritance judgements. Note that, there will be a lot
of $\sigma_1, A_1$ and $\sigma_2, A_2$, and in these cases, $A_1$ is the
result of the sealing of $\sigma_1$, i.e. we assume we have a term
$\goodSeal{\Gamma}{f_1}{\sigma_1}{A_1}$,
$\goodSeal{\Gamma}{f_2}{\sigma_2}{A_2}$ in the premises of judgements
when needed.

@@

The syntax of the inheritance judgement is very close to how Family is
defined in the surface syntax---a Family with no parent is an
inheritance with empty input; an extended Family can be considered as an
inheritance.
% ---because the parent of an extended Family can be overridden
% thus inheritance should only define upon the ``interface'' instead of a
% concrete family. However, since our current formulation doesn't support
% nested inheritance (i.e. we cannot do inheritance inside a family but only top level), our
% formulation still has some distance to the real family polymorphism.

@@

Next, we introduce nested inheritance "inhnest" for dealing with nested families. The rule is mostly direct and we need ``upcasting'' again when dealing with nested family in different but inheriting context.  We also show how to use an inheritance judgement to derive children family and how the beta rule is defined. We omit most of the other substitution laws here.

>>>>

\begin{figure}[!htb]
  \begin{align*}
    &\Gamma~:~"Con"&&\mathboxtext{\goodCtx{\Gamma}{}} &&T~:~"Ty"~\Gamma&&\mathboxtext{\goodType{\Gamma}{T}{}}  &&\gamma~:~"Tms"~\Gamma~\Delta&&\mathboxtext{\goodSub{\Gamma}{\gamma}{\Delta}}  && t~:~"Tm"~\Gamma~T&&\mathboxtext{\goodTerm{\Gamma}{t}{T}} 
  \end{align*}
\caption{Judgements, as Agda types and as presented in this section.}\label{fig:vanillaMLTTjudgeQIIT}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Tm]
      {\goodCtx{\Gamma}{i} \quad \goodType{\Gamma}{T}{j}}
      {\goodTerm{\Gamma}{\_}{T}}
      $$
      $$
      \Rule[name=Tms]
      {\goodCtx{\Gamma}{i} \quad \goodCtx{\Delta}{i}}
      {\goodSub{\Gamma}{\_}{\Delta} \text{ is well-formed}}
      $$
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Con   : Set 
      data Ty    : Con → Set   
      data Tms   : Con → Con → Set 
      data Tm    : (Γ : Con) → Ty Γ  → Set 
    \end{minted}
  \end{minipage}

\caption{Well-formedness rules of the judgements}\label{fig:vanillaMLTTjudgewellformed}
\end{figure}
\underline{\textit{\textbf{Judgements and Universe.}}}
% Judgements in QIIT
We formalize our language as a deep embedding in a type theory using QIIT types. Every judgement is a (dependent) QIIT \textit{type} and all derivations of judgement  are well-typed QIIT terms. (Otherwise how can they be encoded in Agda?) There are four standard judgement forms from (vanilla) MLTT,
well-typed contexts $\goodCtx{\Gamma}{l}$, well-typed types
$\goodType{\Gamma}{T}{l}$, well-typed terms $\goodTerm{\Gamma}{t}{T}$, and
well-typed substitutions $\goodSub{\Gamma}{\gamma}{\Delta}$. The QIITs corresponding of these four judgements are
mutually recursively defined together, and declared in \cref{fig:vanillaMLTTjudgeQIIT}. Our presentation
follows the style of~\citet{kaposi2019gluing} and thus a predicative MLTT, but for readability we
omit the universe levels.
%\YZ{What's the distinction of judgments vs. sequents?}.\EDJreply{I am not sure about the correct terminology here. Here I want to say "even underivable judgement has to be well-typed". That's the main reason I spell out the (pseudo) Agda code there. I actually want the reader to have intrinsic-typed syntax in mind all the time (like read conventional math but acknowledge we are manipulating Agda)}\EDJreply{I rephrase that so there won't be confusion for the future readers. Please check}
Latex-wise, in \cref{fig:vanillaMLTTjudgewellformed}, we spell out these \textit{well-formedness rules} of each
judgement and their (pseudo-)Agda counterparts to make things more accessible. In (pseudo-)Agda, well-formedness rules are just well-typedness of (indexed) QIIT family---(the judgement)"Tm~$\Gamma$~$T$" is well-typed (well-formed) only when $\Gamma$ and $T$ are both well-typed (well-formed). We omitted a bunch for latex version. Of
course, a well-formed judgement is not necessarily derivable, just as
a well-typed QIIT type is not necessarily inhabited. 
These well-formedness rules are direct translations of the \textit{well-typedness} of QIIT.

@@

% How judgemental equality is used
Quotient is used to represent definitional equality (aka judgemental
equality) between QIIT types concisely.
This way, for all four kinds of judgements we are
using, there is always equality among the derivations but only those equalities between terms and types are emphasized due to their non-triviality.

@@

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma~|~"RecSig"~\tau~T \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma~|~"RecSig1"~A~B~T~|\\
    \text{Terms, including Seal}   \quad & t, t_1, t_2, f    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t~|\\ & &&"prjR"~j~o~|~"Wrec"~t_1~t_2~|~"inh"~h~t\\
    \text{Inheritance Structure} \quad & h, h' &&= "inhid"~|~"inhov"~h~t~|~"inhext"~h~t~|~"inhinh"~h~|~"inh"~h~|~"inhnest"~h~h'
  \end{alignat*}\YZ{ What is 'W T'? Do you mean 'c T'?  }\YZreply{Why is Seal not merged into Terms?}\EDJreply{You can see \ruleref{Ind-Type}. For $T : \bW\tau$, $W~T : \cU$, for $\goodType{\Gamma}{T}{}$, $c~T : \cU$ }\EDJreply{Seal can easily mergedd into terms. But seal has a new judgement. Do you want to merge them? }
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}
  \end{align*}
\caption{Extended Judgements, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgements. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

The core language builds on MLTT and adds four new kinds of judgements.
% Among them, sealing judgement $\goodSeal{\Gamma}{\_}{\sigma}{A}$ is just a
% shorthand for term judgement
% $\goodTerm{\Gamma , \cC \sigma}{\_}{A[\pi_1]}$ where $A$ is a type.
% We have shown some exemplar rules for all four standard types of
% judgments. Now we focus on the newly introduced facility. 
We have two kinds of signatures, one for inductive types, the other for linkages. We start with inductive type signature.

@@

\caption{Sealing Judgement, and its Agda Representation (or What do we mean when we say one judgement is a shorthand for the other)}

@@

Next we talk about inheritance judgements. Note that, there will be a lot
of $\sigma_1, A_1$ and $\sigma_2, A_2$, and in these cases, $A_1$ is the
result of the sealing of $\sigma_1$, i.e. we assume we have a term
$\goodSeal{\Gamma}{f_1}{\sigma_1}{A_1}$,
$\goodSeal{\Gamma}{f_2}{\sigma_2}{A_2}$ in the premises of rule
when needed.

@@

The deduction rules of the inheritance judgement is very close to how Family is
defined in the surface syntax---a Family with no parent is an
inheritance with empty input; an extended Family can be considered as an
inheritance.
% ---because the parent of an extended Family can be overridden
% thus inheritance should only define upon the ``interface'' instead of a
% concrete family. However, since our current formulation doesn't support
% nested inheritance (i.e. we cannot do inheritance inside a family but only top level), our
% formulation still has some distance to the real family polymorphism.

@@

Next, we introduce nested inheritance "inhnest" for dealing with nested families. The rule is mostly direct and we need ``upcasting'' again when dealing with nested family in different but inheriting context.  We also show how to use an inheritance judgement and their derivation to construct children family and how the beta rule is defined. We omit most of the other substitution laws here.
